---
title: "MED 5101 - RNA-seq Assignment 2: DESeq2 (Daniel Gladish: 300399445)"
author: "Daniel Gladish (300399445), Perkins Lab, OHRI"
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: true    
    toc_depth: 4 
bibliography: refs.bib # ****DO THIS LATER 
---




Import the necessary libraries.
```{r}
## Load the libraries required for the analysis

# Loading data
library(GEOquery)

# Analysis tools
library(DESeq2)           # Fold change analysis
library(apeglm)           # Method for shrinking fold changes

# Data visualization
library(tidyverse)        # Data munging and visualization (ggplot2)
library(ggrepel)          # Improved labeling of plots
library(pheatmap)         # Pretty Heatmaps
library(EnhancedVolcano)  # Volcano plots
library(RColorBrewer)     # Colour palettes

# R markdown document formatting
library(knitr)
```

Download the data
```{r, eval=FALSE}
    getGEOSuppFiles("GSE144871")
    list.files("GSE144871")
```

import the data
```{r}
    gli3_data<-read.table("./GSE144871/GSE144871_filtered_counts_190926.txt.gz",sep="\t",header=T)

# note that GLI3_data will be a data frame as read.table creates a data frame by default
```




Convert df to mat, and move gene symbols into the row names, as this is the require format for DESeq2


Inspect the data frame
```{r}
print(head(gli3_data))
```

Eliminate the ensembl ID Convert the df to matrix & place the gene symbols (contents of MGI column) in the row names
```{r}
gli3_data$ensembl <- NULL


# select the columns of the data frame I want to keep.
columns_to_keep <- c("ASC.1818", "ASC.246", "ASC.540", "ASC.543", "ASC.928", "ASC.960")

gli3_mat <- as.matrix(gli3_data[, match(columns_to_keep, colnames(gli3_data))])

#check to see if conversion was successful
print(all(colnames(gli3_mat)==columns_to_keep))
```


```{r}
rownames(gli3_mat) <- gli3_data$MGI

# let's eliminate the columns that aren't going to be used in the analysis


# print subset of gli3_mat to see if conversion worked
print(head(gli3_mat))
```


Create table containing metadata (sample names & associated conditions) for each of the samples. NOTE: make sure order of samples names in the vector = order of samples names in the matrix
```{r}
condition <- factor(c(rep("ASC-Gli3", times=3), rep("Control", times=3)), levels=c("Control", "ASC-Gli3"))

sampleTable <- data.frame(data.frame(sample_name=colnames(gli3_mat),condition=condition))
```



```{r}


```




```{r}


```


```{r}

```

